\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Hasyimi Bahrudin}}
	\\
	Kuala Lumpur, Malaysia $\cdot$
	hasyimi@hasyimibahrudin.com $\cdot$
	github.com/hasyimibhar $\cdot$
	linkedin.com/in/hasyimi-bahrudin/
	\\
\end{center}

%==== Summary ====%

\begin{center}
	Senior backend engineer with over 11 years of working experience, with over 5 years of experience working remotely. Love wearing many hats.
\end{center}

%==== Experience ====%
\header{Work Experience}
\vspace{1mm}

\textbf{Beam} \hfill Kuala Lumpur, Malaysia (Remote)\\
\textit{Senior Software Engineer II (Data Platform)} \hfill March 2023 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Promoted to SE2
	\item Lead the implementation of dbt slim CI on top of Argo Workflow
	\item Work closely with operation teams around the world to empower business decisions with data
\end{itemize}
\textit{Senior Software Engineer I (Data Platform)} \hfill October 2022 - February 2023\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Changed team to explore data engineering and analytics
	\item Familiar with BigQuery, ClickHouse, dbt, Argo Workflow
	\item Rolled out Argo Workflow to replace Zapier for business automation, reducing operational cost by 85\%
	\item Improved business metrics alerts using time-series anomaly detection, reducing false positives by 90\%
	\item Migrated ELT workflows to dbt and Argo Workflow, improving data quality and cost control
\end{itemize}
\textit{Senior Software Engineer I (Vehicles)} \hfill May 2021 - September 2022\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Moved to the vehicles team after reorganization. Work on backend projects related to vehicle IOT. Mostly in Go.
	\item Built an IOT simulator, which allows the team to test our services without requiring physical IOT
	\item Helped to reduce 70\% of unnecessary database writes, which was causing frequent downtime due to database bloat
	\item Lead the microservice e2e testing project, which helped to improve developer confidence and productivity as we transition towards microservices. Most breaking changes are now caught before they get merged to master.
	\item Helped to write a query translator for translating Postgresql to BigQuery SQL, which is helping our transition to BigQuery as data lake
\end{itemize}
\textit{Senior Software Engineer I (Product)} \hfill July 2020 - May 2021\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Worked as full stack engineer, writing mostly Typescript (Node.js for backend, React Native for frontend)
	\item Helped roll out 3DS payment in Malaysia, which improved add card success rate for Malaysia from 60\% to 80\%
	\item Optimized PostGIS queries to take advantage of geospatial indexing, which reduced latency and database CPU usage
	\item Implemented OpenAPI to improve API documentation and programmability, which improved developer experience
\end{itemize}

\pagebreak

\textbf{Pollen} \hfill Kuala Lumpur, Malaysia (Remote)\\
\textit{Senior Software Engineer} \hfill January 2020 - May 2020\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item I was part of the pioneer engineers for a small pre-seed startup, writing mostly Typescript
	\item Helped the team to adopt Docker for local development, which improved engineer workflow
	\item Mentored junior engineers through PR reviews
\end{itemize}

\textbf{Perlin} \hfill Singapore (Remote)\\
\textit{Core Engineer} \hfill August 2019 - January 2020\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item I was part of the core team that was implementing the Wavelet distributed consensus protocol
	\item Replaced usage of LevelDB with Badger, which reduced write latency by 10x.
	\item Optimized memory usage when syncing state.
	\item Wrote a lot of tests, which increased test coverage from 40\% to 70\%
\end{itemize}

\textbf{Self-employed} \hfill Kuala Lumpur, Malaysia (Remote)\\
\textit{Freelance Developer} \hfill August 2018 - July 2019\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Took a short break from working with startups
	\item Worked on a few freelance projects
\end{itemize}

\textbf{KATSANA} \hfill Kuala Lumpur, Malaysia\\
\textit{Full Stack Developer} \hfill 2016 - 2018\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item I was part of a team of full stack developers. Used mostly PHP (Laravel).
	\item I led the project of building an in-house IOT server using Go, replacing an open-source server. This improved the overall performance of the product, and also gives us more control on how the server works.
	\item Helped the team to revamp their dashboard to use WebSocket instead of polling, which improved overall performance
\end{itemize}

\textbf{Terato Tech} \hfill Bangi, Malaysia\\
\textit{Games Programmer} \hfill 2012 - 2015\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item I was part of a small team of mobile game developers. Used mostly C++ (cocos2dx).
	\item Built a pseudo-3D game engine (a-la F-Zero) for a mobile badminton game.
	\item Built a mobile game, which is a fusion of tower defense and mining (Minecraft) game. Not published.
	\item Built an online card collecting mobile game for the Japanese market (similar to Fantastica) with a team of 1 game producer, 2 programmers, and 3 game artists. Not published.
\end{itemize}

\pagebreak

%==== Education ====%
\header{Education}
\textbf{Georgia Institute of Technology}\hfill Georgia, Atlanta\\
MS Computer Science \textit{GPA: 3.7} \hfill Fall 2019 - Spring 2023\\
\vspace{2mm}
\textbf{Limkokwing University}\hfill Cyberjaya, Malaysia\\
BS Games Technology \textit{GPA: 3.7} \hfill 2008 - 2011\\
\vspace{2mm}

\header{Skills}
\begin{tabular}{ l l }
	Programming Languages: & Go, Java, Python, C++, C                                     \\
	Areas of interest:     & Distributed computing, High performance computing, Compilers \\
\end{tabular}
\vspace{2mm}

\header{Open Source Contributions}
{\textbf{LLVM}} {\sl C++} \hfill reviews.llvm.org/people/commits/22060/\\
Casual contributor to LLVM as an effort to improve my compilers knowledge.\\
\vspace*{2mm}
{\textbf{Distributed 2D tiled engine}} {\sl Javascript} \hfill github.com/hasyimibhar/voffice-crdt\\
Proof of concept for a distributed 2D tiled engine (virtual office) built on top of CRDT (yjs).\\
\vspace*{2mm}

\header{Personal Interests}
{\textbf{Mechanical keyboards}} \\
I own a split hand ergonomic keyboard, which I hand-wired myself.\\
\vspace*{2mm}
{\textbf{Coffee}} \\
I brew my own coffee (V60, espresso). Recently started roasting my own beans too.\\
\vspace*{2mm}
{\textbf{Guitar}} \\
I started playing guitar in 2020. I mostly play bossa nova on a classical guitar.\\
\vspace*{2mm}
{\textbf{Digital gardening}} \\
I recently started digital gardening. You can read my notes at https://hasyimibahrudin.com.
\ 
\end{document}
